---
title: "Untitled"
author: "Caleb Swing"
date: "12/2/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import Data

```{r}
raw_data <- read.csv("../group_2/CDPHE_COVID19_County-Level_Open_Data_Repository.csv")
covid <- raw_data %>% 
  mutate(COUNTY = as.factor(COUNTY),
         Date = mdy(Date),
         Desc_ = as.factor(Desc_),
         FIPS = as.factor(FIPS),
         FULL_ = as.factor(FULL_),
         LABEL = as.factor(LABEL),
         Metric = as.factor(Metric),
         ObjectId = as.factor(ObjectId),
         POP = as.factor(POP),
         Rate = as.numeric(Rate),
         Value = as.numeric(Value)) %>% 
  rename(county = COUNTY,
         date = Date,
         descriptor = Desc_,
         fips = FIPS,
         full = FULL_,
         label = LABEL,
         metric = Metric,
         objectid = ObjectId,
         population = POP,
         rate = Rate,
         value = Value) %>% 
  select(label, fips, population, descriptor, metric, value, rate, date, objectid) %>% 
  mutate(response = coalesce(value, rate)) %>% 
  select(label, fips, population, metric, response, date)

covid
```

# Time Series with Cases (Sara, Fay)
## State Cumulative

The following summary is the total number of Cases, Deaths, and Rate per 100,000 for the entire state of CO for each day. This dataset will be used to create a Time series line graph with the  Cumulative Cases, Deaths, or Rates for the entire state of CO for each unit of time.

```{r state_cumulative_data}
state_cumulative <- covid %>% 
  filter(metric %in% c("Cases","Deaths", "Rate Per 100,000")) %>% 
  group_by(metric, date) %>% 
  summarize(state_cumulative_total_perday = sum(response)) %>% 
  ungroup()
state_cumulative
```
```{r time_series with cases}
deaths_bar <- state_cumulative %>% 
  filter(metric == "Deaths") %>% 
  ggplot(aes(x = date, y = state_cumulative_total_perday
))+
  geom_line()

cases_line <- state_cumulative %>% 
  filter(metric == "Cases") %>% 
  ggplot(aes(x = date, y = state_cumulative_total_perday
))+
  geom_line()
deaths_bar
cases_line
```

# Colorado County Heat Map (Fay, Caleb)
## County Cumulative
The following summary is the total number of Cases for each county. This dataset will be used to create a heat map ofcumulative covid cases for each county in Colorado.
```{r county_cumulative_data}
covid %>% 
  filter(metric %in% c("Cases")) %>% 
  group_by(label, fips, population) %>% 
  summarize(sum_of_cumulative_cases_percounty = sum(response)) %>% 
  mutate(fips = str_pad(fips, 2, side = "left", pad = "0"),
         fips = str_pad(fips, 3, side = "left", pad = "0"))
```
```{r}
library(tigris)
library(viridis)
state <- covid %>% 
  mutate(STATE_FIPS = str_pad(fips, 2, side = "left", pad = "0"),
         CZ_FIPS = str_pad(fips, 3, side = "left", pad = "0")) %>% 
  unite(fips, STATE_FIPS, CZ_FIPS, sep = "") %>% 
  filter(metric == "Cases") %>% 
  group_by(fips) %>%
  summarize(cases = sum(response)) %>% 
  mutate(cases = as.factor(cases),
         fips = as.factor(fips))
state
co_counties <- counties(state = "CO", cb = TRUE, class = "sf")
class(co_counties)
co_event_counts <- state %>% 
  group_by(fips) %>% 
  count() %>% 
  ungroup()
ggplot() + 
  geom_sf(data = co_event_counts, aes(fill = n)) + 
  scale_fill_viridis(name = "Number of events\n(2017)"
state %>% 
ggplot() + 
  geom_sf(data = co_counties, aes(fill = cases)) +
    scale_fill_viridis(name = "Number of events\n(2017)")
ggplot() + 
  geom_sf(data = state, aes(fill = cases)) + 
  scale_fill_viridis(name = "Number of events\n(2017)")
```

# Callender Heat Map (Tyler, Sara)
## State Difference
This dataset represents the daily increases of Test for the entire state of COlorado for each day.

```{r}
covid %>% 
  filter(metric == "Total Tests Performed") %>% 
  group_by(date) %>% 
  summarize(cumulative_test_state_perday = sum(response)) %>% 
  mutate(test_perday = cumulative_test_state_perday - lag(cumulative_test_state_perday)) %>% 
  select(date, test_perday)
```

